% !TeX spellcheck = en_US
% Review Christian Stary January 2020
% Merge mit Thomas Schaller Pfad Chapter 4

% testcomment

\RequirePackage{snapshot}

\documentclass[11pt, showtrims, final, oldfontcommands]{memoir}
% Resolve conflict between functions in class memoir and package changes
\let\classadded\added 	 % save the class’ definition
\let\added\relax		 % ‘undefine’ \foo
\let\deleted\relax    % neutralize \deleted command
\let\comment\relax    % neutralize \comment command



\usepackage[T1]{fontenc}
\usepackage[textsize=footnotesize]{todonotes}

\usepackage{morewrites}

% prepare package changes for managing the review process
\usepackage[draft, markup=underlined, highlightmarkup=background]{changes}
\definechangesauthor[name= Albert Fleischmann, color=green]{AF}
\definechangesauthor[name= Werner Schmidt, color=blue]{WS}
\definechangesauthor[name= Robert Singer, color=cyan]{RS}
\definechangesauthor[name= Christian Stary, color=purple]{CS}
\definechangesauthor[name= Andre Wolski, color=magenta]{AW}
\definechangesauthor[name= Stephan Borgert, color=orange]{SB}
\definechangesauthor[name= Matthes Elstermann, color=pink]{ME}
\definechangesauthor[name= Thomas Schaller, color=violet]{TS}
\definechangesauthor[name= alle anderen, color=lightgray]{STAR}

\usepackage{soulutf8}
\usepackage{soul}

\usepackage{memsty}
\usepackage{memlays}
\usepackage{titlepages}
\usepackage{dpfloat}
\usepackage{fonttable}[2009/04/01]
\usepackage{sidecap}
\usepackage{wrapfig}
\usepackage[htt]{hyphenat}
\usepackage{lscape}
\usepackage{listings}
\usepackage{enumitem}
\usepackage{longtable}
\usepackage{pdfpages}
\usepackage{caption}

\usepackage{amssymb}
\usepackage{program}
\usepackage{mathtools}
\usepackage{graphicx}
\usepackage{minted}

\usepackage{xargs}                      % Use more than one optional parameter in a new commands
\usepackage{xcolor}  % Coloured text etc.









\newmintinline[asminline]{lexer.py:CoreASMLexer -x}{escapeinside=~~}

\setlistdepth{9}

\setlist[itemize,1]{label=$\bullet$}
\setlist[itemize,2]{label=$\bullet$}
\setlist[itemize,3]{label=$\bullet$}
\setlist[itemize,4]{label=$\bullet$}
\setlist[itemize,5]{label=$\bullet$}
\setlist[itemize,6]{label=$\bullet$}
\setlist[itemize,7]{label=$\bullet$}
\setlist[itemize,8]{label=$\bullet$}
\setlist[itemize,9]{label=$\bullet$}

\renewlist{itemize}{itemize}{9}

% Use the built-in division styling
\headstyles{memman}

% BoD bietet zwei Grossformate an: A4 und etwas kleiner
% Springer empfiehlt 24 x 17
\setstocksize{29.7cm}{21cm}

% size of the page after trimming the typeblock
% Springer Textfeld inkl. Kopfzeile 20.5 x 13.5
\settrimmedsize{29.7cm}{21.0cm}{*}

% lines of text
\settypeblocksize{50\onelineskip}{32pc}{*}

% Stocksize ist deckungsgleich mit Druckbereich
\setlength{\trimtop}{0pt}
\setlength{\trimedge}{\stockwidth}
\addtolength{\trimedge}{-\paperwidth}

% Margins
%\setulmargins{2.0cm}{*}{*}
%\setlrmargins{2.0cm}{*}{*}

%\setheadfoot{\onelineskip}{\onelineskip}
%\setheaderspaces{*}{\onelineskip}{*}

%\setmarginnotes{17pt}{3cm}{\onelineskip}

%\sideparmargin{outer}
%\sidecapmargin{outer}

\checkandfixthelayout[lines]

\title{Standard for the Subject-oriented\\ Specification of Systems}
\author{Stephan Borgert, Matthes Elstermann, Albert Fleischmann, \\ Reinhard Gniza, Herbert Kindermann, Florian Krenn,\\ Christian Stary, Werner Schmidt, Robert Singer, Florian Strecker, Andr\'e Wolski}

% ToC down to subsections
\settocdepth{subsection}
% Numbering down to subsections as well
\setsecnumdepth{subsection}

% extra index for first lines
%\makeindex[lines]

% keine Links anzeigen
\hypersetup{
	colorlinks=false,
	pdfborder={0 0 0},
}

\renewcommand*{\sideparfont}{\normalfont\footnotesize}

\include{mathdef}

\begin{document}

\chapterstyle{veelo}

\frontmatter

\pagestyle{empty}

% half-title page
\vspace*{3cm}
\begin{adjustwidth}{0cm}{-3cm}
	\begin{flushright}
		\LARGE\textsf {Standard for the Subject-oriented\\Specification of Systems}
	\end{flushright}
\end{adjustwidth}
\vspace*{\fill}
\cleardoublepage

% title page
\vspace*{0cm}
\begin{flushleft}
	\Large\textsf{Albert Fleischmann \textit{Editor}}\par
\end{flushleft}
\vspace{2cm}
\begin{flushleft}
	\Huge\textsf{Standard for the Subject-oriented\\Specification of Systems}\par
	\bigskip\bigskip
	\Large\textsf{Working Document}
\end{flushleft}
\vspace{2.5cm}
\begin{flushleft}
	%\normalsize\textsf{With 178 Figures}
\end{flushleft}
\vspace*{\fill}
\clearpage

% copyright page
\begingroup
\footnotesize
\setlength{\parindent}{0pt}
\setlength{\parskip}{\baselineskip}
% Platz
\vspace*{3cm}
% Autoren
\begin{flushleft}
	Egon B\"orger\\
	xyz\\
	\medskip
	Stephan Borgert\\
	xyz\\
	\medskip
	Matthes Elstermann\\
	xyz\\
	\medskip
	Albert Fleischmann\\
	InterAktiv Unternehmensberatung, Pfaffenhofen a.d. Ilm, Germany\\
	\medskip
	Reinhard Gniza\\
	xyz\\
	\medskip
	Herbert Kindermann\\
	xyz\\
	\medskip
	Florian Krenn\\
	xyz\\
	\medskip
	Thomas Schaller\\
	xyz\\
	\medskip
	Werner Schmidt\\
	Technische Hochschule, Ingolstadt, Germany\\
	\medskip
	Robert Singer\\
	FH JOANNEUM--University of Applied Sciences, Graz, Austria\\
	\medskip
	Christian Stary\\
	Johannes Kepler Universit\"at, Linz, Austria\\
	\medskip
	Florian Strecker\\
	xyz\\
	\medskip
	Andr\'e Wolski\\
	Technische Universit\"at, Darmstadt, Germany\\
	\medskip
	Conny Zebold\\
	Technische Hochschule, Ingolstadt, Germany\\
\end{flushleft}
\vspace*{\fill}
This work is subject to copyright. All rights are reserved, whether the whole or part of the material is concerned, specifically the rights of translation, reprinting, reuse of illustrations, recitation, broadcasting, reproduction on microfilm or in any other way, and storage in data banks. Duplication of this publication or parts thereof is permitted only under the provisions of the German Copyright Law of September 9, 1965, in its current version. Violations
are liable to prosecution under the German Copyright Law.\par
\textcopyright{ 2020} Institute of Innovative Process Management, Ingolstadt\par
The use of general descriptive names, registered names, trademarks, etc. in this publication does not imply, even in the absence of a specific statement, that such names are exempt from the relevant protective laws and regulations and therefore free for general use.\par
Typeset by the authors\par
Production and publishing: XYZ\par
ISBN: 978-3-123-45678-9 (dummy)
\endgroup
\clearpage

\pagestyle{companion}

\setupshorttoc
\tableofcontents
\cleardoublepage

\chapter{Commands for Reciew process}
For managing changes the package change is used. Following commands are essential:\\
\textbf{Mark text without id:}\\
\hl{
	This is the way  text is marked
}\\

\textbf{Add todo withaout id:}\\
Here is some text
\todo{The original todo note withouth changed colours.\newline Here's another line.} Here is some text
\newline
\newline
\newline
\newline
\textbf{Add todo withaout id and inline:}\\
Here is some text
\todo[inline]{The original todo note withouth changed colours.\newline Here's another line.} Here is some text
\newline

\textbf{Add text with id:}\\
\added[id=AF, comment=remarks to added text]{Added text}\\

\textbf{Delete command with id:}\\
\deleted[id=WS, comment=example for delete]{Here is the text to be deleted}
Here is some text\\
\newline
\textbf{Replace text with id:}\newline
Here is some text
\replaced[id=CS, comment=Remarks to Replace text]{new text}{old text}
Here is some text\\

\textbf{highlight text with id:}\\
Here is some text
\highlight[id=AF, comment=remarks]{highlighted text}\\

\textbf{Add todo with fancy line but without id:}\\
Here is some text \todo[color=green!40, fancyline]{The original todo note.\newline Here's another line with a fancy line}
 Here is some text
\newline 
\newline
\newline
\newline 
\newline
\newline
For todo commands ids are not allowed. For the add, highlight and
Documentation for using the changes package can be found:\\
http://ctan.ebinger.cc/tex-archive/macros/latex/contrib/changes/changes.english.pdf
\newline
The ids and colors for the various reviewers can be found in the preamble (line 29-33) of the text file.

\chapter{Preface}
This book is a collection of all the essential aspects of subject oriented modeling and programming. Many parts of this documents are copy pasts of various books and papers. Table \ref{tbl:sources} shows the sources for the various chapters and sections.\\
In chapter 1 an overview is given to subject orientated language PASS and the methods which are used to describe its structural and execution semantics. OWl (Web Ontology Language) \cite{Web:OWL} is used to describe the structural semantics and Abstract State Machines (ASM) \cite{book:ASM-2018}, \cite{book:ASM-2003} is applied to specify the execution demantics precisely.\\
In chapter 2 the structure of PASS specification is considered in detail and its semantic is defined precisely in a formal way using OWL and ASM. The semantic of the execution of PASS models is described in chapter 3. The execution semantic uses coreASM which is an executable extension of the ASM method. This means that models described in PASS can be executed by a coresponding interpreter.\\
Chapter 4 shows how the abstract implementation independent PASS models can be implemented using software components, physical components or human.  A formal language is described how the right ressources are assigned to the entities of the model.\\
In the last chapter some additional aspects of the subject oriented modeling approach is considered. Thes aspects extend the kernel which was defined in chapter 2, 3 and 4.\\
The appendix contains the details of the formal semantic of PASS. Appendix A contains the complete Ontology, Abbendix B defines the mapping of the ontology to the ASM definition of PASS and Appendix C containes the complete formal execution semantics.


\include{preface}




\cleardoublepage

\setupparasubsecs
\setupmaintoc
\tableofcontents
\setlength{\unitlength}{1pt}
\cleardoublepage

%\listoffigures
%\clearpage
%\listoftables

%\lipsum{2}

%===================================

\mainmatter

\include{chapter01}
\include{chapter02}
\include{chapter03}
\include{chapter04}
\include{chapter05}
\include{appendix}

\backmatter

%\bibliographystyle{IEEEtran}
\bibliography{Standard}

\listoftodos
\listofchanges[style=list, show=all]


\end{document}
